### 2014-03-15 docs/paper.tex
GAE could stand for other systems.

@@

\section{Other third-party services}

>>>>

Most of the discussion in this paper will use the specific example of the
Google frontend server as a front for App Engine.
App Engine is the system on which we have based our deployment,
and it suffices to illustrate the concept of domain fronting.
There are other systems, discussed in Section~\ref{sec:otherservices}
that can be substituted for App Engine, with few or no modifications.
When an example talks about ``App Engine,'' the reader may instead think
of other systems such as the CloudFlare content delivery network.

@@

\section{Other third-party services}
\label{sec:otherservices}
